Duration Analysis for Performing-Dynamics performances

### 2021-07-05 material/expstimuli/analysis/expression/stim_a/duration.Rmd
bar plots >> box plots
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Plot
#### Bar chart
- Error bars show SD of the mean

```{r duration_bar,  echo = FALSE}
p_duration <- ggplot(data = duration, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Normalised Duration", subtitle = "Duration: Performing-Articulation")
p_duration
```

>>>>

### Plot
#### Box plot

```{r duration_bar,  echo = FALSE}
duration_trial <- dt_duration[Subcomponent == "Legato" | Subcomponent == "Staccato", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr, TrialNr, Subcomponent)]

p_duration <- ggplot(data = duration_trial, aes(x = SubNr, y = Mean)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Normalised Duration", subtitle = "Duration: Performing-Articulation")
p_duration
```

### 2021-07-05 material/expstimuli/analysis/expression/stim_d/duration.Rmd
bar plots >> box plots
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Plot
#### Bar chart
- Error bars show SD of the mean

```{r duration_bar,  echo = FALSE}
p_duration <- ggplot(data = duration, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Normalised Duration", subtitle = "Duration: Performing-Dynamics")
p_duration
```

@@

>>>>

### Plot
#### Box plot

```{r duration_bar,  echo = FALSE}
duration_trial <- dt_duration[Subcomponent == "Forte" | Subcomponent == "Piano", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr, TrialNr, Subcomponent)]

p_duration <- ggplot(data = duration_trial, aes(x = SubNr, y = Mean)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Normalised Duration", subtitle = "Duration: Performing-Dynamics")
p_duration
```

@@

# Included performances for averaging
## Legato
```{r outlier_leg, echo = FALSE}
# for legato
duration_trial_leg <- dt_duration[Subcomponent == "Legato", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr, TrialNr)]
duration_trial_leg
```

## Staccato
```{r outlier_sta, echo = FALSE}
# for staccato
duration_trial_sta <- dt_duration[Subcomponent == "Staccato", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr, TrialNr, Subcomponent)]
duration_trial_sta
```
